Syntax and Semantics of Abstract Binding Trees

### 2015-12-02 paper.tex
Add more citations

\begin{remark}
  The presentation we have given above is related both to the Schanuel topos
  and, equivalently, Pitts' category of nominal sets \cite{fiore-staton:2006}; we differ only in
  discussing sheaves on $\SCtxSite$, as
  opposed to sheaves on $\OpCat{\SymSets}$ (i.e.\ unisorted contexts).
\end{remark}

@@

For any Grothendieck site $\Match{\mathfrak{S}}{\Pair{\mathcal{C}}{J}}$, the
inclusion $\Of{\iota}{\Sheaves{\mathfrak{S}}\ra\Presheaves{\mathcal{C}}}$ of
sheaves into presheaves has a left adjoint
$\IMode{\Sheafify{(-)}}\dashv\IMode{\iota}$, which takes any presheaf
$\Of{X}{\Presheaves{\mathcal{C}}}$ to a unique sheaf
$\Of{\Sheafify{X}}{\Sheaves{\mathfrak{S}}}$, called the \emph{sheafification}
of $X$. Sheafification is the twice-iterated application of the
\emph{+-construction} $X^+$, which turns a presheaf into a separated presheaf,
and a separated presheaf into a sheaf:
\begin{align*}
  \ADefine{
    X^+(C)
  }{
    \int^{S\in J(C)}
    \Hom{\Presheaves{\mathcal{C}}}{S}{X}
  }\\
  \ADefine{
    \Sheafify{X}
  }{
    X^{++}
  }
\end{align*}

>>>>

\begin{remark}
  The presentation we have given above is related both to the Schanuel topos
  and, equivalently, Pitts' category of nominal sets \cite{fiore-staton:2006,
  pitts:2013}; we differ only in discussing sheaves on $\SCtxSite$, as opposed
  to sheaves on $\OpCat{\SymSets}$ (i.e.\ unisorted contexts).
\end{remark}

@@

For any Grothendieck site $\Match{\mathfrak{S}}{\Pair{\mathcal{C}}{J}}$, the
inclusion $\Of{\iota}{\Sheaves{\mathfrak{S}}\ra\Presheaves{\mathcal{C}}}$ of
sheaves into presheaves has a left adjoint
$\IMode{\Sheafify{(-)}}\dashv\IMode{\iota}$, which takes any presheaf
$\Of{X}{\Presheaves{\mathcal{C}}}$ to a unique sheaf
$\Of{\Sheafify{X}}{\Sheaves{\mathfrak{S}}}$, called the \emph{sheafification}
of $X$. Sheafification is the twice-iterated application of the
\emph{+-construction} $X^+$, which turns a presheaf into a separated presheaf,
and a separated presheaf into a sheaf \cite{mac-lane-moerdijk:1992}:
\begin{align*}
  \ADefine{
    X^+(C)
  }{
    \int^{S\in J(C)}
    \Hom{\Presheaves{\mathcal{C}}}{S}{X}
  }\\
  \ADefine{
    \Sheafify{X}
  }{
    X^{++}
  }
\end{align*}
